Quality Control Report
========================================================


```{r,include=F, echo=F}
require(RCurl)
eval( expr = parse( text = getURL(
    "https://raw.githubusercontent.com/oganm/toSource/master/ogbox.R",
    ssl.verifypeer=FALSE) ))
parent = getParent(2)
setwd(parent)

sourceGithub("BiGCAT-UM", "affyQC_Module", "functions_imagesQC.R")

source('runVars.R')

humanDesign = read.table('Data/humanCellTypeDesign.tsv',header=T,sep='\t', stringsAsFactors=F)


gsms = humanDesign[,1]

gsms = strsplit(gsms,',')


platforms = unique(humanDesign$Platform)

require(affy)

affies = lapply( rep("AffyBatch", len(platforms)), new )
celsInFolder = list.files('humanCellTypeCel')
celsNoExtension = gsub('[.](C|c)(E|e)(L|l)','',celsInFolder)

for (i in 1:len(platforms)){
    toRead = unlist(gsms[humanDesign$Platform %in% platforms[i]])
    relevant = celsInFolder[celsNoExtension %in% toRead]
    affies[i] = ReadAffy(filenames = paste0('humanCellTypeCel/',relevant))
}

names(affies) = platforms
affies
```


This file contains the quality control information on the chips we used and choose not to use. 

We were able to find limited amounts of human cell type specific data but they were shown to be of very poor quality. The sources and GEO IDs of these datasets can be found from [this](/Data/humanCellTypeDesign.tsv) file

Human Cell Type Data
-------------
Human data was found on 3 chips `platforms r`. Below, the percentages of MM>PM signals on each chip group can be found
```{r,warning=FALSE}
 
lapply(affies,function(x){
    mean(mm(x)>pm(x))
})
```

Per chip ratio of MM>PM vs overall pm+mm intensity

```{r, warning = F}
lapply(affies,function(x){
data = data.frame(MMPM = rep(0,len(x)), intensity = rep(0,len(x)))
for (i in 1:len(x)){
    data$MMPM[i] = mean(mm(x[,i]) > pm(x[,i]))
    data$intensity[i] = mean(pm(x[,i])+mm(x[,i]))
}
plot(data$MMPM,data$intensity)

}
)


```


A quite messy plots of density distributions. Note that there are multiple batches in the same chip 
```{r,warning=F}
ground = lapply(affies,hist)
```

And RNA degredation plots with mean slopes
```{r,warning=FALSE}
ground = lapply(affies, function(x){
    deg = AffyRNAdeg(x)
    print(mean(deg$slope))
    plotAffyRNAdeg(deg)
})

```

In the first plot we notice a single sample with quite a low slope and decided to see the raw image file for that chip. Which turned out to be an unusually homogenous image

```{r, warning=FALSE}
deg = AffyRNAdeg(affies[[1]])
image(affies[[1]][,order(deg$slope)[1]])
```


A similar outlier also exists in the 3rd chip type
```{r, warning=FALSE}
deg = AffyRNAdeg(affies[[3]])
image(affies[[3]][,order(deg$slope)[1]])
```


Mouse Cell Type
------------------
Lets proceed to our lovely mouse data, that has two platforms

```{r,include=F, echo=F}
parent = getParent(2)
setwd(parent)
 design = read.table('Data/Design.tsv',quote='',header=T,sep='\t')

    design = design[!is.na(design[,namingCol]),]

    gsms = regmatches(design[, 1], gregexpr(celRegex, design[, 1],perl=T))
    if (any(lapply(gsms,len)==0)){
        print('No cel names could be captured from the following rows')
        print((1:len(gsms))[lapply(gsms,len)==0])
    }

    platforms = unique(design$Platform)

    affies = lapply( rep("AffyBatch", len(platforms)), new )
    names(affies) = platforms
rma
    #create a vector of affy objects based on how many chips are there just works with 2 right now
    #implementation of a third generation is straightforward. in fact i could have done it instead
    #of writing this but oh well...
    for (i in 1:len(affies)){
        celsInFolder = list.files(
            paste0(celDir,'/',platforms[i]))
        celsNoExtension = gsub('[.](C|c)(E|e)(L|l)','',celsInFolder)
        gsms = regmatches(design[design$Platform == platforms[i], 1], gregexpr(celRegex, design[design$Platform == platforms[i], 1],perl=T))
        gsms = unlist(gsms)

        relevant = celsInFolder[celsNoExtension %in% gsms]

        affies[i] = ReadAffy(filenames = paste0(celDir,'/',platforms[i],'/',relevant))
    }
affies
```



```{r,warning=FALSE}
lapply(affies,function(x){
    mean(mm(x)>pm(x))
})

lapply(affies,function(x){
data = data.frame(MMPM = rep(0,len(x)), intensity = rep(0,len(x)))
for (i in 1:len(x)){
    data$MMPM[i] = mean(mm(x[,i]) > pm(x[,i]))
    data$intensity[i] = mean(pm(x[,i])+mm(x[,i]))
}
plot(data$MMPM,data$intensity)

}
)

ground = lapply(affies,hist)

ground = lapply(affies, function(x){
    deg = AffyRNAdeg(x)
    print(mean(deg$slope))
    plotAffyRNAdeg(deg)
})



```

